Large scale agile transformations: A literature review

### 2013-01-24 tex/article.tex
Fixed "applicability of agile" in challenges

@@

        \raggedright\rule{0pt}{0.4cm}Applicability of agile in the organization  &
            Conflicts with business (eg. planning) [S6, S11, S21] \newline
            Suitability for non-development (testing, maintenance, etc.) [S2, S4, S13]\newline
            Conflicts with other functions [S6, S10, S11, S13] \\

@@

"Applicability of agile problem" --> Paremmin "ongelmaa" kuvaava ilmaisu
--> Myös keskimmäinen pointti
--> "Other functions" --> tarkemmin

>>>>

Typical challenges and and success factors reported in the studies are listed in
Table \ref{table:success}.

@@

        \raggedright\rule{0pt}{0.4cm}Effect of agile outside of development  &
            Conflicts with business (eg. planning) [S6, S11, S21] \newline
            Making non-development functions agile (testing, maintenance, etc.) [S2, S4, S13]\newline
            Conflicts with other functions (marketing, HR, etc.) \newline[S6, S10, S11, S13] \\

@@
